---
title: "R Markdown Presentation & Plotly"
author: "Rajesh Solanki"
date: "October 11, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

# Load data file

```{r}
library(plotly)
library(dplyr)
mydata <- read.csv("datafile.csv", header=TRUE, sep=",")
```
# Create data frame
```{r}
mydata <- data.frame(mydata)
names(mydata)<-c("State", "Population", "Poverty(%)")
mydata <- data.frame(State = mydata$State, Population = as.vector(mydata$Population), Pov= as.vector(mydata$`Poverty(%)`))
mydata$Abb <- with(mydata, paste(state.abb))
```

# Create hover text
```{r}
mydata$hover <- with(mydata, paste(State, '<br>', "Population:", Population,"Million",'<br>',"Poverty:",Pov,"%"))
```
# Make state borders red and Set up some mapping options
```{r}
borders <- list(color = toRGB("red"))
map_options <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)
```
# Finally plot the map

```{r}
plot_ly(z = mydata$Population, text = mydata$hover, locations = mydata$Abb, 
        type = 'choropleth', locationmode = 'USA-states', 
        color = mydata$Population, colors = 'Blues', marker = list(line = borders)) %>%
  layout(title = 'US Population and % poverty in each state  as per Census 2017 Estimate', 
         geo = map_options)
```



